Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 Paper.Rmd
finished editing Q3 for now (expect more changes later) several things for Shya to do, see comments in all docs

### Need to think about mechanisms for biogeochemical, evolutionary, and community data

@@

For green spruce aphid abundance data, *Ceratium furca* abundance data, and methane-flux
data, because these datasets exhibited lower-tail dependence 
(Table \ref{tab_multivar_summary}), we compared empirical and surrogate skewness values
via a one-tailed test in the left tail: the $p$-value result was simply the fraction
of surrogate skewnesses less than the skewness computed from the empirical data. For
leaf-curling plum aphid first flight data, because this dataset exhibited upper-tail 
dependence (Table \ref{tab_multivar_summary}), we did the analogous one-tail test
in the right tail.

<!--Reminder that Table 2 says:
Green spruce - lower tail
Leaf-curling - upper tail
Cerratium - lower tail
methane - marginal lower tail-->

<!--***DAN: stopped here in this section, 2019 02 12, 633am-->

We also showed **(ii)** asymmetric copula structure affected slope of spatial Taylor's Law differently than as expected from symmetric Normal copula (For details see Appendix \ref{SM-Consequence_TL_simulation}). For example, our model simulation showed lower tail dependent Clayton copula had much higher slope (spatial-Taylor's law) than symmetric Normal copula, which in turn had higher slope than upper tail dependent Survival Clayton family (Fig. \ref{SM-fig_spTL}(I)). In the following section we will show application of these ideas with real data sets.

@@

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Red dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}
<!--***DAN: Shya, please replace the x axis label by "Skewness" and the y-axis label
by "Frequency"-->

<!--***DAN: stopped here in this section, 2019 02 12, 633am-->

We used our four multivariate data sets : aphid-count data, aphid-first flight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We carried out the analysis mentioned in the concepts above for spearman preserving surrogates, with aphid abundance and aphid first flight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. For example, Figure \ref{fig_skewness_spearman} represents the results for each data set with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the green-spruce aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the nonparametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was significantly higher than expected if the leaf-plum curling aphid first flight data came from a normal copula, which was also confirmed by upper-tail dependence results from model selection and nonparametric results (see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on nonparametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was found significantly lower in comparison to its Normal surrogates (Figure \ref{fig_skewness_spearman} D). 
<!--We found the same result with all data sets when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}). Now we did only with spearman preserving to handle ties and +ve semidefinite case-->

## Results for \hyperref[Intro]{\textbf{(Q3)}}: Change of curvature of spatial Taylor's law regression line

@@

Spatial Taylor's law, the observed linear relationship between `log`(variance) and `log`(mean) of population densities of a species from different locations, is a well-known pattern found in ecology and related fields [@Taylor1961, @Taylor1988, @Cohen2013, @Doring2015, @Kuo2016, @Xu2016, @Reuman2017]. We already showed through simulation (Appendix \ref{SM-Consequence_TL_simulation}) that for asymmetric copula this linear relationship somehow deviates compared to Normal copula for a distribution with gamma marginals. We tested spatial Taylor's law with aphid count data (for all 20 species) and found that the mean curvature of the regression line from `log`(variance) vs. `log`(mean) of population abundance data was significantly different from $10000$ Normal surrogates (Spearman-correlation and marginal distribution preserving) for $20\%$ of total species considered. For example, the "Corn leaf aphid" (having significantly upper tail dependence from model selection and nonparametric analysis) showed mean curvature of regression line close to zero, whereas `r 10000 -(tlsp6$p_left_mncurv*10000)` of the $10000$ Normal surrogates showed higher curvature, indicating here Normal copula didn't hold linear relationship between `log`(spatial variance) and `log`(spatial mean) (see Fig \ref{fig_sTL_mncurv_sp6}).

\begin{figure}[!h]
\textbf{ \hspace{4 cm} (A) \hspace{4 cm} (B) \hspace{4 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=10 cm]{./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf}
\includegraphics[width=5 cm]{./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf}\\
\caption{log(spatial variance) and log(spatial mean) for $(A)$ corn-leaf aphid (\textit{Rhopalosiphum maidis}) abundance and for $(B)$ one of the $9961$ Normal surrogates (having same marginal distribution and Spearman correlation of actual data). $(C)$ Histogram of mean curvature of $10000$ normal surrogates showed that for corn-leaf aphid abundance data (with asymmetric tail dependence), Normal surrogates didn't follow linear relationship between log(spatial variance) and log(spatial mean). \label{fig_sTL_mncurv_sp6}}
\end{center}
\end{figure}

>>>>

<!--***DAN: Maybe need to think about mechanisms for biogeochemical, evolutionary, and community data-->

@@

For green spruce aphid abundance data, *Ceratium furca* abundance data, and methane-flux
data, because these datasets exhibited lower-tail dependence 
(Table \ref{tab_multivar_summary}), we compared empirical and surrogate skewness values
via a one-tailed test in the left tail: the $p$-value result was simply the fraction
of surrogate skewnesses less than the skewness computed from the empirical data. For
leaf-curling plum aphid first flight data, because this dataset exhibited upper-tail 
dependence (Table \ref{tab_multivar_summary}), we did the analogous one-tailed test
in the right tail.

Pursuing ideas that sprang from earlier theoretical work [@Reuman2017], we tested whether
the copula structure of dependence between population variables influences the
spatial version of Taylor's
law. Taylor's law is an extremely commonly observed and widely studied 
[@Taylor1961, @Taylor1988, @Cohen2013, @Xu2016] empirical pattern that relates the 
variances of groups, $g$, of population measurements to the means of these 
groups via a power law, $v_g = a \times m_g^b$, or equivalently via a log-log linear 
relationship, $\log(v_g)=\log(a)+b \times \log(m_g)$. Here $b$ is called 
the Taylor's law *exponent* or 
*slope*. There are several versions of Taylor's law. For spatial Taylor's law,
given population density or abundance data $x_i(t)$ measured in locations
$i=1,\ldots,N$ and times $t=1,\ldots,T$, a group $g$ consists of 
all the measurements $x_i(t)$, $i=1,\ldots,N$ made in different locations at the same time.
So the means and variances in the Tayor's law formula are computed across 
space. Taylor's law has been 
verified in data from hundreds of taxa and has been applied in numerous fields
including fisheries management, estimation of species persistence times, and
agriculture [@Cohen2015,@Reuman2017].

We tested whether the linearity of the spatial Taylor's law relationship was partly
due to the copula structure of the dependences between the populations sampled. 
Using corn leaf aphid abundance data as an example, but also
applying the same analysis to the abundance data we had for 19 other aphid species
(see *Data*), we calculated the curvature (details in Appendix \ref{SM-TL_curvature}) 
of the empirical Taylor's law relationship; Taylor's law hypothesizes that this 
curvature should be close to 0. We then calculated the same curvature quantity for
10000 surrogate datasets, using the same surrogate procedure described above in 
this section, and compared the empirical Taylor's law curvature to the 
distribution of surrogate curvatures using a two-tailed test. If the empirical
curvature value was below the $5^{\text{th}}$ quantile of the surrogate distribution, 
then copula structure contributes to the linearity of spatial Taylor's law 
because randomizing copula structure while retaining other statistical properties
of the data cause the Taylor's law relationship to become significantly more 
curved.

<!--***DAN: Shya,  want to add the extinction risk stuff back in, let's discuss-->

@@

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Red dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}
<!--***DAN: Shya, please replace the x axis label by "Skewness" and the y-axis label
by "Frequency" in the above plot-->

Skewness results were generally consistent with hypotheses. For the datasets that
exhibited strong lower-tail (respectively, upper-tail) 
dependence in earlier analyses (namely, the green spruce 
aphid abundance data for lower-tail, and the leaf-curling plum aphid first flight data
for upper-tail, Table 
\ref{tab_multivar_summary}), the skewness, through time, of the spatial average of the 
empirical data was less than (respectively, greater than) a significant fraction (i.e.,
more than $95\%$) of the
surrogate skewness values 
(Fig. \ref{fig_skewness_spearman}A,B). For the datasets that demonstrated a 
more moderate lower-tail dependence in earlier analyses (the 
\emph{Ceratium furca} abundance and the methane data), skewness of the spatial
average showed a non-significant tendency toward being less than surrogate skewnesses
(Fig. \ref{fig_skewness_spearman}C), or was less than a marginally significant 
fraction of surrogate skewnesses (Fig. \ref{fig_skewness_spearman}D).

@@

Results also suggested that copula structure contributes to the linearity of 
spatial Taylor's law. For instance, the spatial Taylor's law relationship 
for corn leaf aphid abundance data was significantly less curved than for 
surrogate datasets (Fig. \ref{fig_sTL_mncurv_sp6}). Three of $20$ aphid species
had cuvatures less than at least $95\%$ of surrogate datasets ($p=X$, $Y$, $Z$ for 
the $A$, $B$ and $C$ species, respectively). 
<!--***DAN: Shya, please fill in X, Y, Z, A, B, C with autolinks)-->
Three such significant
results of 20 species could have occurred by chance due to 
multiple-testing error. However, for each of the 20 species, we computed the fraction
of surrogate curvatures less than the curvature that came from real data, and we
combined these $p$-values using Fisher's combined probability test to get an
aggregate $p$-value of $0.019$ 
<!--***DAN: Shya, see the Wikipedia article on Fisher's method to learn about it. Then 
you need to put this analysis into the code suite and have the resulting p value
typed in above be an autolink instead. Here is what I did: 
1) I copied by hand all the pleft values on the pdf you sent me into a vector pleft. Instead you should create such a vector in your code from your test output, not typing in the results.
2) I used the formula stat<--2*sum(log(pleft)) to get the Fisher method statistic
3) I compared to a chi-squared distribution with 40 degress of freedom using 1-pchisq(stat,40) to get my p-value
Please let me know if any of this is unclear.-->
for the test of the null hypothesis that 
copula structure did not contribute to linearity of Taylor's law for any of the 
species. This result is usefully suggestive and can guide future work, but still does not
provide certainty, because the Fisher method provides $p$-values that are too 
small if its assumption of independent tests is violated. Though our 20 species
have different host plants so may be independent for the purposes of our analyses, 
it would be difficult to fully assess independence.
<!--***DAN: Shya, can you remind me why the same analyses were not done for plankton,
if there is a good reason? Or if you did it, what were the results?--> 
We provide simulation results in Appendix \ref{SM-Consequence_TL_simulation}
that robustly illustrate, at least in the model setup we used, 
that copula structure influences spatial Taylor's law.

\begin{figure}[!h]
\textbf{ \hspace{4 cm} (A) \hspace{4 cm} (B) \hspace{4 cm} (C)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=10 cm]{./Results/taylorslaw_results/aphid_count_sp6_logv_vs_logm.pdf}
\includegraphics[width=5 cm]{./Results/taylorslaw_results/aphid_count_sp6_sTL_mncurv.pdf}\\
\caption{Mean curvature of the spatial Taylor's law relationship for 
corn leaf aphid abundance
data (A) was significantly less than for surrogates (B, C). The Taylor's law 
relationship for one example surrogate (B) shows shows greater curvature than
for data (A), and the significance of the difference was demonstrated
by the fact that only $39$ of $10000$ surrogates had curvature less than that
of the data (C). See Appendix \ref{SM-TL_curvature} for details on 
how curvature was calculated.\label{fig_sTL_mncurv_sp6}}
\end{center}
\end{figure}
<!--***DAN: Shya, pls make the x axis label on C read simply "Mean curvature"-->

<!--***DAN: I want to put back in some extinction risk results. Let's talk about this, please, Shyamolina-->

### 2019-02-12 SupportingInformation.Rmd
finished editing Q3 for now (expect more changes later) several things for Shya to do, see comments in all docs

```{r tab_plankton_info, echo=F, results='asis',message=F}
library(tibble)
plankton_info <- tibble(c('Calanus I-IV','Para-Pseudocalanus spp','Temora longicornis','Acartia spp',
                          'Centropages typicus',
                          'Oithona spp','Echinoderm larvae','Calanus finmarchicus',
                          'Calanus helgolandicus','Metridia lucens','Decapoda larvae',
                   'Euphausiacea','Thalassiosira spp','Rhizosolenia styliformis',
                   'Ceratium fusus','Ceratium furca','Ceratium tripos','Ceratium macroceros',
                   'Rhizosolenia alata alata','Pseudocalanus elongatus Adult',
                   'Nitzschia delicatissima','Nitzschia seriata')
)
knitr::kable(plankton_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 22 plankton taxa for which data were available \\label{tab_plankton_info}",
      col.names = c("Plankton taxon name"))
```

@@

<!--\newpage-->
```{r tab_temp_aphid_p_CvM, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_CvM,
             format='latex',
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_CvM}",
             booktabs=TRUE
             )
```

<!--\newpage-->
```{r tab_temp_aphid_p_KS, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_KS,
             format='latex',
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_KS}",
             booktabs=TRUE
             )
```

<!--\newpage-->
```{r tab_temp_aphid_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw,
             format='latex',
             caption = "Model-averaged lower tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTdep_AICw}",
             booktabs=TRUE
             )
```

<!--\newpage-->
```{r tab_temp_aphid_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$UTdep_AICw,
             format='latex',
             caption = "Model-averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_UTdep_AICw}",
             booktabs=TRUE
             )
```

<!--\newpage-->
```{r tab_temp_aphid_LTmUT, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw - RES_temp_aphid$UTdep_AICw,
             digits = 5,
             format='latex',
             caption = "Model averaged lower tail dependence minus model averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTmUT}",
             booktabs=TRUE
             )
```

<!--# Cause of non-Normal copula structure : the Moran effect and copula structure in populations \label{Cause_Moran}-->

<!--
## Asymmetric sensitivity and copula structure in populations
           ----moved to Paper.Rmd----
-->

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman")
hist(answer2s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer2s$realskw,y=0,col="black",pch=15,cex=2)

p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer3s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer3s$realskw,y=0,col="black",pch=15,cex=2)

p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=F,
                           corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

# Consequence of non-Normal copula structure : Effect on Taylor's law \label{Consequence_TL_simulation}

Here, we examined the nature of the slope and how it changed if population time series (taken as $50$ years) from different locations (say, $numloc=25$) had some certain type of copula structure (namely, \textbf{C}, \textbf{F} and \textbf{SC}) other than the $\textbf{N}$ormal copula. First, we simulated (N $\times$ n $\times$ nr) dimensional normal copula with co-variance $\rho =0.7$, where $(N=50,n=25,nr=10)$ are the length of time series, number of sampling locations and number of replica for that copula, respectively. Then we generated Kendall-correlation preserving \textbf{C}layton, \textbf{F}rank and $\textbf{S}$urvival \textbf{C}layton surrogates with same dimension of \textbf{N}ormal. With these four different types of copula we computed `log`(spatial variance) and `log`(mean) and plotted in Fig.\ref{fig_spTL}(A-D). We also tested statistically that whether linearity, homoskedasticity is maintained in each copula data set or not and plotted our results along with root mean square error, intercept and slope in Fig.\ref{fig_spTL}(E-I). We did a quadratic regression with each simulated copula for all types and measured quadratic coefficient and mean curvature for the regression line which is plotted in Fig.\ref{fig_spTL}(J-K) (For code see [`copsurrognd.R`](https://github.com/sghosh89/BIVAN/blob/master/copsurrognd.R) and [`TaylorsLawTools.R`](https://github.com/sghosh89/BIVAN/blob/master/TaylorsLawTools.R)).

>>>>

```{r tab_plankton_info, echo=F, results='asis',message=F}
library(tibble)
plankton_info <- tibble(c('Calanus I-IV','Para-Pseudocalanus spp','Temora longicornis','Acartia spp',
                          'Centropages typicus',
                          'Oithona spp','Echinoderm larvae','Calanus finmarchicus',
                          'Calanus helgolandicus','Metridia lucens','Decapoda larvae',
                   'Euphausiacea','Thalassiosira spp','Rhizosolenia styliformis',
                   'Ceratium fusus','Ceratium furca','Ceratium tripos','Ceratium macroceros',
                   'Rhizosolenia alata alata','Pseudocalanus elongatus Adult',
                   'Nitzschia delicatissima','Nitzschia seriata')
)
knitr::kable(plankton_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 22 plankton taxa for which data were available \\label{tab_plankton_info}",
      col.names = c("Plankton taxon name"))
```
<!--***DAN: These names differ from those used in Emma's 2016 Glob Change Biol paper.
Need to check with Chris Reid. Have to get this right.-->

@@

<!--
```{r tab_temp_aphid_p_CvM, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_CvM,
             format='latex',
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_CvM}",
             booktabs=TRUE
             )
```
-->

<!--
```{r tab_temp_aphid_p_KS, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$gfc_p_KS,
             format='latex',
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for **negative average winter temperature data**. Tests were based on bootstrapping as described in Methods.\\label{tab_temp_aphid_p_KS}",
             booktabs=TRUE
             )
```
-->

<!--
```{r tab_temp_aphid_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw,
             format='latex',
             caption = "Model-averaged lower tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTdep_AICw}",
             booktabs=TRUE
             )
```
-->

<!--
```{r tab_temp_aphid_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$UTdep_AICw,
             format='latex',
             caption = "Model-averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_UTdep_AICw}",
             booktabs=TRUE
             )
```
-->

<!--
```{r tab_temp_aphid_LTmUT, echo=F, results='markup'}
knitr::kable(RES_temp_aphid$LTdep_AICw - RES_temp_aphid$UTdep_AICw,
             digits = 5,
             format='latex',
             caption = "Model averaged lower tail dependence minus model averaged upper tail dependence statistic for each location pair for **negative average winter temperature data**.\\label{tab_temp_aphid_LTmUT}",
             booktabs=TRUE
             )
```
-->

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman")

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

# Calculating curvature for Taylor's law \label{TL_curvature}

<!--***DAN: Shya, I need a reminder how we did this, can you please tell me where the
code is, then I can write this section. Feel free to take a stab at it yourself, too,
though.-->

# Effects of non-N copula structure on Taylor's law \label{Consequence_TL_simulation}

<!--***DAN: Dan has not edited this section yet at all-->
Here, we examined the nature of the slope and how it changed if population time series (taken as $50$ years) from different locations (say, $numloc=25$) had some certain type of copula structure (namely, \textbf{C}, \textbf{F} and \textbf{SC}) other than the $\textbf{N}$ormal copula. First, we simulated (N $\times$ n $\times$ nr) dimensional normal copula with co-variance $\rho =0.7$, where $(N=50,n=25,nr=10)$ are the length of time series, number of sampling locations and number of replica for that copula, respectively. Then we generated Kendall-correlation preserving \textbf{C}layton, \textbf{F}rank and $\textbf{S}$urvival \textbf{C}layton surrogates with same dimension of \textbf{N}ormal. With these four different types of copula we computed `log`(spatial variance) and `log`(mean) and plotted in Fig.\ref{fig_spTL}(A-D). We also tested statistically that whether linearity, homoskedasticity is maintained in each copula data set or not and plotted our results along with root mean square error, intercept and slope in Fig.\ref{fig_spTL}(E-I). We did a quadratic regression with each simulated copula for all types and measured quadratic coefficient and mean curvature for the regression line which is plotted in Fig.\ref{fig_spTL}(J-K) (For code see [`copsurrognd.R`](https://github.com/sghosh89/BIVAN/blob/master/copsurrognd.R) and [`TaylorsLawTools.R`](https://github.com/sghosh89/BIVAN/blob/master/TaylorsLawTools.R)).
